For this moment to materialize, I owe thanks to many people, so many that a sheet here would be little, in a summarized way I will try to thank everyone.

For first I will be eternally grateful to UTFPR itself, which opened the doors giving me the opportunity to study in one of the best public institutions in Brazil. I thank you not only for the financial aid, which, incidentally, was fundamental for this moment to happen, but above all I thank you immensely for the warmth, the human warmth to me dispensed in the great majority by your teachers and servants and workers in general of the UTFPR. I am quite convinced that it would not have happened the other way.

By the second, I want to thank all my teachers, and those who in one way or another, even though not being my teacher, have always been on my side and taught me everything that was possible. Here the list is great, beginning with the teachers of mathematics, I owe a lot of thanks to Professor Fausto, they were years of coexistence in design, Professor Diego, Professor Cleverson, Professors Neusa and Rafaela, Professor Lucas. Many thanks also to my beloved computer teachers, Claudio Bazzi, Cezar Angonese, Nelson Betzek, Paulo Job, Alessandra Hoffmann, Fernando Schutz, Allan Gavioli, Paulo Lopes, Márcio Matté, Evandro Pessini, Hamilton Pereira, Jorge Aikes, Juliano Lamb, Arnaldo Candido, Neylor Michel, Patrícia Lopez, Ricardo Sobjack, Everton Coimbra, José Airton, Silvana Mendonça, Lairton Moacir, Elias Lira. I am and will forever be grateful to you all.

Besides my dear teachers, I would like to thank my classmates, who helped me a lot during the course, among all, which are not many, I would like to thank Gabriela Michellon and Samanta de Sousa very much. Last, companion not only of the academic works but also companion for the uncertain hours. Thank you very much to all of you.

Thirdly, I would like to thank those responsible for this project, Dr\textordfeminine. Tania, Professor Dr Pedro and Professor Dr\textordfeminine. Deisy, who have entrusted me with this project, giving me the opportunity to contribute to a significant project. Thank you very much, it was a unique and rewarding experience to have had the honor of working with you.

In particular, I would like to thank Dr. Arnaldo Candido for his patience always dedicated to me, not only regarding doubts regarding the subjects, but also incredible help in the articles, at the conclusion of this work and going beyond the academic subjects, giving me strength in the hours that But I needed it. Here is all my gratitude and admiration for Professor Dr. Arnaldo.

%Lastly and most importantly, I want to thank Dr\textordfeminine. Marisa and Dr. Pedro Luiz, two very special people. Unfortunately, I will never be able to thank them as much as they helped me, because there is no way to measure what these two special people have done and still do for me, I can only leave here a simple thank you and say that I will always be extremely grateful, Forever in my heart.
%
%My thanks to everyone for making it possible to turn a great dream into reality.